\LARGE \bf Simultaneous Coordinate Calibrations by Solving the AX=YB Problem without Correspondence*

### 2015-06-28 Tex_AXYB/paper.tex

In most cases, the homogeneous transformations with $As$ and $Bs$ are given based on the data from different sensors. Due to asynchronous timing of the measurement transmissions, the correspondences between $A_{i}$ and $B_{i}^{k}$ is unknown. The advantage of the above probabilistic solution lies on that $X$ and $Y$ can be calculated even if without any a priori knowledge of the correspondence. However, there are still eight possible candidate results $(X_{i},Y_{i})$. Using Euclidean-Group invariants, it is straightforward to determine which pair is the correct one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.

The Discrete Fourier Transform (DFT) decomposes a time-domain signal into its constituent frequencies. The input is a finite list of equally spaced samples of a function. Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}{x_{n}}$

\begin{equation}\label{equ21}
    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa)
\end{equation}
The Inverse Discrete Fourier transform (IDFT) denoted by

\begin{equation}\label{equ22}
    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa)
\end{equation}

@@

\begin{equation}\label{equ23}
    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau)
\end{equation}

In convolution theorem, the Fourier transform of a convolution is the product of the Fourier transforms, namely,

\begin{equation}\label{equ24}
    f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)]
\end{equation}

The correlation theorem indicates that the correlation function, $Corr(f,g)$, will have a large value at a shift vector if the two sequences $f$ and $g$ contain similar features. The correlation can be obtained based on the convolution theorem. The DFT of the correlation $Corr(f,g)$ is equal to the product of the DFT of a sequence $f_{n}$ and the complex conjugate $\mathcal{F}^{*}$ of the DFT of the other sequence $g_n$.

\begin{equation}\label{equ25}
    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}]
\end{equation}

Compared with the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).

There are two sequences $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$ from each pair $(A_{i},B_{i}^{k})$. For homogeneous transformations from which the range of $\theta$ can vary, two sequences $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ can be first normalized.

\begin{equation}\label{equ26}
    \theta_{1}=\frac{(\theta_{A_{i}}-\mu_{A_{i}})}{\sigma_{A_{i}}}, \theta_{2}=\frac{(\theta_{B_{i}^{k}}-\mu_{B_{i}^{k}})}{\sigma_{B_{i}^{k}}}
\end{equation}

where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the average of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.

Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $(n)$ which describes the probability that these two sequences are separated by this particular unit. The location of the function maximum indicates the amount of shift, $\tau_{shift}$, between the two sequence $\theta_{A_{i}}$ and $\theta_{B_{i}^{k}}$.

@@

Therefore, the correspondence between the two sequences can be found. The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$. The data stream can be shifted to reach correspondence once the shift is found and the correct solution can also be found by minimizing the absolute deviations based on Euclidean-Group invariants relations using the method in Section \ref{sect2}.

@@

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig3.eps}
\caption{
$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ \ $x_i \sim \mathcal{N}(0,0.1)$.
}
\label{fig2}
\end{figure}
\end{center}

>>>>

In most cases, the homogeneous transformations  $\{A_i\}$ and $\{B_j\}$ are calculated based on the data obtained from different sensors. Due to the asynchronous timing of the sensor readings, the correspondences between $\{A_{i}\}$ and $\{B_{j}^{k}\}$ is usually unknown. This section deals with the case where there is a shift between $\{A_i\}$ and $\{B_j\}$, and Euclidean-Group invariants are used to recover the correspondence between the data streams. {\color{red}The advantage of the above probabilistic solution lies in that $X$ and $Y$ can be calculated even if there is not a priori knowledge of the correspondence.} However, there are still eight possible candidates of $(X_{k},Y_{k})$ to choose from and by using Euclidean-Group invariants, it is straightforward to determine which pair is the optimal one if the correspondence between $A_{i}$ and $B_{i}^{k}$ can be known.

The Discrete Fourier Transform (DFT) decomposes a time-domain signal into its constituent frequencies. The input is a finite list of equally spaced samples of a function. Given a discrete signal consisting of a sequence of $N$ complex numbers $x_{0},x_{1},\cdots,x_{N-1}$, the DFT is denoted by $X_{\kappa} = \mathcal{F}({x_{n}})$ as:

\begin{equation}\label{equ21}
    X_{\kappa} = \sum_{n=0}^{N-1}x_{n}\cdot exp(-i\frac{2\pi}{N}n\kappa).
\end{equation}
The Inverse Discrete Fourier transform (IDFT) is denoted as:

\begin{equation}\label{equ22}
    x_{n} = \frac{1}{N}\sum_{n=0}^{N-1}X_{\kappa}\cdot exp(i\frac{2\pi}{N}n\kappa).
\end{equation}

@@

\begin{equation}\label{equ23}
    (f \ast g)(\tau)=\sum_{i=0}^{N}f(t_{i})g(t_{i}-\tau).
\end{equation}

In the convolution theorem, the Fourier transform of a convolution is the product of the Fourier transforms, namely:

\begin{equation}\label{equ24}
    f \ast g = \mathcal{F}^{-1} [\mathcal{F}(f) \cdot \mathcal{F}(g)].
\end{equation}

The correlation theorem indicates that the correlation function, $Corr(f,g)$, will possess a larger value for a shift vector where the two sequences $f_n$ and $g_n$ can share more similar features. The correlation can be obtained based on the convolution theorem. The DFT of $Corr(f,g)$ is equal to the product of the DFT of $f_{n}$ and the complex conjugate $\mathcal{F}^{*}$ of the DFT of $g_n$:

\begin{equation}\label{equ25}
    Corr(f,g)=f \star g = \mathcal{F}^{-1}[\mathcal{F}(f) \cdot (\mathcal{F}(g))^{*}].
\end{equation}

Compared to the standard time-domain convolution algorithm, the complexity of the convolution by multiplication in the frequency domain is significantly reduced with the help of the convolution theorem and the fast Fourier transform (FFT).

Given two sequences $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$ corresponding to  $\{A_{i}\}$ and $\{B_{i}^{k}\}$, the shift that is needed to recover the data correspondence is obtained as below. 
Firstly, $\theta_{Ai}$ and $\theta_{B_{i}^{k}}$ are normalized as:

\begin{equation}\label{equ26}
    \theta_{1}=\frac{(\theta_{A_{i}}-\mu_{A_{i}})}{\sigma_{A_{i}}}, \theta_{2}=\frac{(\theta_{B_{i}^{k}}-\mu_{B_{i}^{k}})}{\sigma_{B_{i}^{k}}}
\end{equation}
where $\mu_{A_{i}}(\mu_{B_{i}^{k}})$ is the mean of $\theta_{A_{i}}(\theta_{B_{i}^{k}})$ and $\sigma_{A_{i}}(\sigma_{B_{i}^{k}})$ is the standard deviation.

Here, the correlation function $Corr(\theta_{1},\theta_{2})$  is the function of the time sequence index $(n)$ which describes the probability that these two sequences are separated by this particular unit. The index corresponding to the maximum of $Corr(\theta_{1},\theta_{2})$  indicates the amount of shift $\tau_{shift}$ between the $\{\theta_{A_{i}}\}$ and $\{\theta_{B_{i}^{k}}\}$.

@@

Therefore, the correspondence between the two sequences can be found. {\color{red}The data of $\theta_{A_{i}}$ or $d_{A_{i}}$ are shifted by $-\tau_{shift}$ to obtain a sequence of new pairs $(\theta_{A_{i}}(i+\tau_{shift}),\theta_{B_{i}^{k}})$ and $(d_{A_{i}}(i+\tau_{shift}),d_{B_{i}^{k}})$, $max(i,i+\tau_{shift})\leq i \leq min(i,i+\tau_{shift})$ TO BE REPHRASED}. The data stream can be shifted back to regain correspondence once the shift is computed and the correct solution of $X$ and $Y$ can also be recovered by minimizing the cost function Eq.(\ref{equ23}) using Euclidean-Group invariants as shown in Section \ref{sect2}.

@@

\begin{center}
\begin{figure}
\centering
\includegraphics[width=2.6in]{fig3.eps}
\caption{
$Bs$ are randomly generated using  $B_i=B_{init}exp(\widehat{\mathbf{x}})$,$\mathbf{x}=(x_1,\dots,x_6)^T $ where $x_i \sim \mathcal{N}(0,0.1)$.
}
\label{fig2}
\end{figure}
\end{center}
